intro

### 2022-02-02 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
corrected file names
changed location of acknowledgements etc.

``` {r child = "intro.Rmd"}
```

```{r child = "method.Rmd"}
```

>>>>

``` {r child = "TheoreticalBackground.Rmd"}
```

```{r child = "Method.Rmd"}
```

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup

\newpage

# Acknowledgements

This research is partly funded by the German Research Foundation (DFG) as part of the Collaborative Research Center (CRC) 940.
Additionally, we have applied for funding of the participants' compensation from centralized funds of the Faculty of Psychology at Technische Universität Dresden.
Applications for the centralized funds will be reviewed in May.
Regardless of whether or not this additional funding will be granted, the study can commence immediately.
The funders have/had no role in study design, data collection and analysis, decision to publish or preparation of the manuscript.

# Author Contributions

CS, AS, and JZ conceptualized the study and its methodology.
CS and JZ acquired funding, investigated, administered the project, and wrote the software.
CS, JZ, and AG did the formal analysis.
CS and JZ visualized the results, and prepared the original draft.
All authors reviewed, edited, and approved the final version of the manuscript.

# Competing Interests

The authors declare no competing interests.
